Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-07-05 Response.tex

\item 
    \begin{itshape}
It appears from equation 5 and your control input definition that you control is unbounded?  Later on in reading the paper I found that you do add bounds on the control.  You may want to indicate earlier on in the paper (closer to eq. 5) that bounds will be added to the control.
\end{itshape}

An additional comment has been included mentioning that the control is assumed to be bounded in magnitude.

\begin{correction}
\ldots and the control inputs is defined as \( \vecbf{u} = \begin{bmatrix} u_x & u_y \end{bmatrix}^T \in \R^{2\times1} \) and assumed to be continuously variable but bounded in magnitude, i.e. \( \vecbf{u}^T \vecbf{u} \leq u_{max}^2 \).
\end{correction}

\item 
    \begin{itshape}
Figure 1 should probably have "axis equal" applied to it.  For that matter, please check all trajectory plots (those which plot the position state), and ensure that all plots are using "axis equal".  If not, please regenerate those plots. 
\end{itshape}

All of the figures showing position states have been modified to use \texttt{axis equal}.

\item 
    \begin{itshape}
Section 3.1 has been discussed in many references, the reader may want to direct them to this material.
(Choose one of Marsden or West's papers for example.)
\end{itshape}

The discussion on the variational integrators has been reduced. 
Much of the background material on Lagrangian mechanics is removed and an additional paragraph is included to summarize the key ideas of variational integrators. 
The additional paragraph is shown below.

\begin{correction}
Geometric numerical integration deals with numerical integration methods which preserve the geometric properties of the flow of a differential equation, such as invaraint properties and symplecticity.
Variational integrators are constructed by discretizing Hamilton's principle rather than the continuous Euler-Lagrange equations.
As a result, integrators developed in this manner have the desirable properties that they are symplectic and momentum preserving.
In addition, they exhibit improved energy behavior over long integration periods.
A thorough discussion of variational integrators is provided in~\cite{west2004,marsden2001}.
We use this approach to construct a variational integrator for the PCRTBP with the inclusion of low-thrust propulsion.

Consider the autonomous mechanical system described by the Lagrangian, \( L(q, \dot{q} ) \), for the generalized coordinates, \( q\) and velocities \( \dot{q} \).
The integration of the continuous Lagrangian along a path, \( q (t) \), followed by the system must satisfy Hamilton's principle, which results in the well-known Euler-Lagrange equations~\cite{lanczos1970}.
In the discrete time scenario, the continuous path \( q(t), \dot{q}(t) \), is replaced by a finite difference approximation over a fixed time step, e.g. \( q_0, \frac{q_1 - q_0}{h} \), which converges to the true velocity as \( h \) tends towards zero.
In this manner, we define a discrete Lagrangian, \( L_d (q_0, q_1, h) \) which approximates the integral of the true Lagrangian over the time interval \( h \) between \( q_0 \) and \( q_1\)~\cite{marsden2001}.
\end{correction}

The second-order trapezoidal rule will give significantly poorer state vector accuracy with respect to a high-precision RK integrator, even if the state is guaranteed to lie on an energy surface.  Why didn't the authors consider going to a higher-order variational integrator, or even a Taylor Integrator?  It is very likely that the integration accuracy will introduce some errors in the accuracy of the partial derivatives and in the states.
Section 3.2 - please cite a reference as to where the selected quadrature rules presented in Table 1 have been derived.

### 2017-07-05 manuscript.tex
Reduce discussion about variational integrators
Reviewer 1 comment 13

The discrete equations of motion for the PCRTBP are derived by choosing an appropriate quadrature rule to discretize the Lagrangian in~\cref{eq:lagrangian}.
In this work, we apply the trapezoidal rule, which allows for an explicit second order accurate approximation of the continuous Lagrangian.
The discrete Lagrangian is given by

>>>>

Consider the autonomous mechanical system described by the Lagrangian, \( L(q, \dot{q} ) \), for the generalized coordinates, \( q\) and velocities \( \dot{q} \).
The integration of the continuous Lagrangian along a path, \( q (t) \), followed by the system must satisfy Hamilton's principle, which results in the well-known Euler-Lagrange equations~\cite{lanczos1970}.
In the discrete time scenario, the continuous path \( q(t), \dot{q}(t) \), is replaced by a finite difference approximation over a fixed time step, e.g. \( q_0, \frac{q_1 - q_0}{h} \), which converges to the true velocity as \( h \) tends towards zero.
In this manner, we define a discrete Lagrangian, \( L_d (q_0, q_1, h) \) which approximates the integral of the true Lagrangian over the time interval \( h \) between \( q_0 \) and \( q_1\)~\cite{marsden2001}.

The discrete equations of motion for the PCRTBP are derived by choosing an appropriate quadrature rule to discretize the continuous Lagrangian in~\cref{eq:lagrangian}~\cite{marsden2001}.
In this work, we apply the trapezoidal rule to approximate the action integral over a fixed time interval.
The trapezoidal rule allows for a second order accurate approximation and alleviates the difficulties in applying implicit quadrature schemes.
The discrete Lagrangian for the PCRTBP is given by
